### 2018-09-06 sections/objects.tex
simple textual changes

Jets containing $b$-hadrons are identified ($b$-tagged) via an algorithm~\cite{Aad:2015ydr,ATL-PHYS-PUB-2016-012} 
that uses multivariate techniques to combine information about the impact parameters of displaced tracks and the  topological properties 
of secondary and tertiary decay vertices reconstructed within the jet. For each jet, a value for the multivariate $b$-tagging discriminant is 
calculated. In the $\Htautau$ search, a jet is considered $b$-tagged if this value is above the threshold corresponding to
an average 70\% efficiency to tag a $b$-quark jet, with a light-jet\footnote{Light-jet refers to a jet originating from the hadronisation of a light quark 
($u$, $d$, $s$) or a gluon.} rejection factor of $\sim$381 and a charm-jet rejection factor of $\sim$12, as determined for jets with
$\pt >20~\gev$ and $|\eta|<2.5$ in simulated $\ttbar$ events. In contrast, the $\Hbb$ search employs a tighter $b$-tagging requirement, 
corresponding to an average efficiency of 60\% to tag a $b$-quark jet, and light-jet and charm-jet rejection factors of 1539 and 34, respectively.

>>>>

Jets containing $b$-hadrons are identified ($b$-tagged) via an algorithm~\cite{Aad:2015ydr,ATL-PHYS-PUB-2016-012} 
that uses multivariate techniques to combine information about the impact parameters of displaced tracks and the  topological properties 
of secondary and tertiary decay vertices reconstructed within the jet. For each jet, a value for the multivariate $b$-tagging discriminant is 
calculated. In the $\Htautau$ search, a jet is considered $b$-tagged if this value is above the threshold corresponding to
an average 70\% efficiency to tag a $b$-quark jet, with a light-jet\footnote{Light-jet refers to a jet originating from the hadronisation of a light quark 
($u$, $d$, $s$) or a gluon.} rejection factor of $\sim$381 and a charm-jet rejection factor of $\sim$12, as determined for jets with
$\pt >20~\gev$ and $|\eta|<2.5$ in simulated $\ttbar$ events. In contrast, the $\Hbb$ search employs a tighter $b$-tagging requirement, 
corresponding to an average efficiency of 60\% to tag a $b$-quark jet, and light-jet and charm-jet rejection factors of 1538 and 34, respectively.

### 2018-09-06 sections/statistical_analysis.tex
simple textual changes

The test statistic $q_\mu$ is defined as the profile likelihood ratio: 
$q_\mu = -2\ln({\cal L}(\mu,{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and ${\hat{\theta}}_\mu$ are the values of the
nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
A related statistic is used to determine the compatibility of the observed data with the background-only hypothesis (i.e.~the discovery test)  
by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
The $p$-value (referred to as $p_0$) representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
above the observed value of $q_0$ in the data. 
%The observed $p_0$-value is checked for each explored signal scenario.
In the case of the data being compatible with the background expectation, upper limits on $\mu$, and thus on 
$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

>>>>

The test statistic $q_\mu$ is defined as the profile likelihood ratio: 
$q_\mu = -2\ln({\cal L}(\mu,{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and ${\hat{\theta}}_\mu$ are the values of the
nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
A related statistic is used to determine the compatibility of the observed data with the background-only hypothesis (i.e.~the discovery test)  
by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
The $p$-value (referred to as $p_0$) representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
%the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
the distribution of $q_0$ based on the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
above the observed value of $q_0$ in the data. 
%The observed $p_0$-value is checked for each explored signal scenario.
In the case of the data being compatible with the background expectation, upper limits on $\mu$, and thus on 
$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.
